Capstone Movielens Report

### 2025-11-23 reports/capstone-movielens.site/05.appendix.Rmd
Function described: get_best_param.result.

##### Signature
\
```{r eval=FALSE}
get_best_param.result <- function(param_values, rmses){
  # ...

  c(param.best_value = param_values[best_pvalue_idx], 
    best_RMSE = rmses[best_pvalue_idx])

##### Arguments
\
A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.

  - **param_values:** A vector containing the values of the input parameters for tuning;; 
  - **rmses:** A vector containing values of the corresponding `Root Mean Squared Errors`..

##### Details
\
Extracts the best values from the input data and returns them as a vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_.

##### Value
\
A vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_:
```{r eval=FALSE}
c(param.best_value, best_RMSE)
```

##### Source Code
\
The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) function is shown below:
```{r eval=FALSE}
get_best_param.result <- function(param_values, rmses){
  best_pvalue_idx <- which.min(rmses)
  c(param.best_value = param_values[best_pvalue_idx], 
    best_RMSE = rmses[best_pvalue_idx])
```

::: {.noteblock data-latex=""}
The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) script on _GitHub_.
:::

@@

  1. Calculates the step size for partitioning the interval into a sequence of $\lambda$ values as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L240):
```{r eval=FALSE}
    seq_increment <- (seq_end - seq_start)/interval_divisor 
```

@@

  Otherwise, makes sure that the minimum *RMSE* value determined so far is no less than the minimum *RMSE* value calculated for the current iteration (`best_RMSE >= min_RMSE`) and goes to [step ?](#).

  Otherwise, **stops execution** with the error message (considers a fatal error!):
```{r eval=FALSE}
    if (best_RMSE == min_RMSE) {
      warning("Currently computed minimal RMSE equals the previously reached best one: ",
              best_RMSE, "
Currently computed minial value is: ", min_RMSE)

@@

  Otherwise, proceeds to the [next step](#func.model.tune.param_range.details.step14):
```{r eval=FALSE}
    if (best_RMSE == min_RMSE) {

@@

::: {.noteblock data-latex=""}
To retrieve the best results for the current iteration from the data stored in the local variable `tuned.result`, the helper function [get_best_param.result] described above is used.
:::
:::

@@

::: { #func.model.tune.param_range.details.finalizing .sidebar }
###### Finalizing Execution
\

Finally, the algorithm initializes the objects to be included in the return list with the results obtained during execution and returns the list to the client code:
```{r eval=FALSE}
  # Finalizing execution:
  n <- length(tuned.result$parameter.value)

@@

The complete source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L208) is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L208) script on _GitHub_.
:::

>>>>

Selects the best values from a pair of matched vectors: a vector of sorted *regularization parameter* $\lambda$ values and a vector of *Root Mean Squared Errors (RMSE)* values passed in the [param_values](#func.tune.model_param.args.param_values) and [RMSEs](#func.get_best_param.result.args.RMSEs) arguments, respectively.

```{r eval=FALSE}
        param_values.best_result <-
          get_best_param.result(tuned.result$parameter.value,
                                tuned.result$RMSE)
```
:::

A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.

::: { #func.get_best_param.result.args.param_values .sidebar }
  - **param_values:** Numeric vector containing a sorted list of the *regularization parameter* $\lambda$ values to search for the best one during the *Model Regularization* process;

:::
::: { #func.get_best_param.result.args.RMSEs .sidebar }
  - **RMSEs:** *RMSE* values computed during the *Model Regularization* process.

This is a *utility function* used to select the *best values* during the *Model Regularization* process utilizing the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].

With this approach the best value of the *regularization parameter* $\lambda$ (we call this the *best value of the regularization parameter* or the *best value of $\lambda$*) is considered to be the value corresponding to the minimum value of the *RMSE* for the model being tested.

In *This Project* this function is used internally in the [model.tune.param_range](#func.model.tune.param_range) function described in *This Section* below.
:::

Numeric vector containing a pair of values: the best *regularization parameter* $\lambda$ value and corresponding *minimal RMSE* 
:::

The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) function is shown below:
```{r eval=FALSE}
get_best_param.result <- function(param_values, RMSEs){
  best_pvalue_idx <- which.min(RMSEs)
  c(param.best_value = param_values[best_pvalue_idx], 
    best_RMSE = RMSEs[best_pvalue_idx])
}
```

::: {.noteblock data-latex=""}
The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) script on _GitHub_.
:::
:::

@@

  1. Calculates the step size for partitioning the interval into a sequence of $\lambda$ values and save it to the local variable `seq_increment` as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L240):
```{r eval=FALSE}
    seq_increment <- (seq_end - seq_start)/interval_divisor 
```

@@

  - Otherwise, makes sure that the minimum *RMSE* value determined so far is no less than the minimum *RMSE* value calculated for the current iteration (`best_RMSE >= min_RMSE`) and goes to [step ?](#).

  - Otherwise, **stops execution** with the error message (considers a fatal error!):
```{r eval=FALSE}
    if (best_RMSE == min_RMSE) {
      warning("Currently computed minimal RMSE equals the previously reached best one: ",
              best_RMSE, "
Currently computed minial value is: ", min_RMSE)

@@

  - Otherwise, proceeds to the [next step](#func.model.tune.param_range.details.step14):
```{r eval=FALSE}
    if (best_RMSE == min_RMSE) {

@@

::: {.noteblock data-latex=""}
To retrieve the best results for the current iteration from the data stored in the local variable `tuned.result`, the helper function [get_best_param.result](#func.get_best_param.result) described above is used.
:::
:::

@@

::: { #func.model.tune.param_range.details.finalizing .sidebar }
###### ***Finalizing Execution***
\

Finally, the algorithm initializes the objects to be included in the return list with the results obtained during execution and returns the *list object* to the client code:
```{r eval=FALSE}
  # Finalizing execution:
  n <- length(tuned.result$parameter.value)

@@

The complete source code of the function [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L208) is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L208) script on _GitHub_.
:::
